---
author: "Demo"
date: "`r format(Sys.Date(), '%m/%d/%Y')`"
output:
  word_document:
    reference_docx: C:/Users/ygrund/ygrund_C_Users/PROJECTS/20210504_NWMOD/Demo/data/Report_Template.docx
    keep_md: yes
    toc: yes
    fig_caption: yes
    fig_width: 12
    fig_height: 6
  officedown::rdocx_document:
  html_document:
    toc: yes
    df_print: paged
---

---
title: "`r paste0("Modeling Quality Assurance Project Plan for the ", qapp_project_area, " Temperature Total Maximum Daily Load")`"
---

```{r, label=`setup`, include=FALSE}
options(knitr.duplicate.label = 'allow')
options(knitr.kable.NA = '')
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(results = "asis",
                      warning = FALSE,
                      error = FALSE,
                      message = FALSE,
                      autodep = TRUE)

library(knitr); library(kableExtra)
library(officedown);library(officer)
library(tidyverse)
library(captioner)
library(readxl)
library(lubridate)
library(flextable)
library(sf); library(sp)
library(rgdal)
library(ggplot2)
library(stringr);library(stringi)
library(english)
library(pacman)
library(httr)

tbls  <- captioner::captioner(prefix="Table")
figs <- captioner::captioner(prefix="Figure")
eqns <- captioner::captioner(prefix="Equation")

```

# Introduction

This Quality Assurance Project Plan (QAPP) summarizes the modeling approach to be used for the `r qapp_project_area` Temperature Total Maximum Daily Load (TMDL) replacement project.

A TMDL is a water quality restoration plan and the calculation of the maximum amount of a pollutant that a waterbody can receive while still meeting water quality standards for that particular pollutant. A TMDL establishes a pollutant-reduction target and allocates the maximum amount of pollutant load reductions necessary to the contributing source(s) of the pollutant. The Clean Water Act requires TMDLs be developed for waterbodies that do not meet water quality standards and are listed as water quality impaired on the State’s 303(d) list.

In 2012, The U.S. District Court found that EPA’s approval of an element of Oregon’s water quality standard for temperature, the Natural Conditions Criteria, was unlawful. The Natural Conditions Criterion stated that where the natural thermal potential of all or a portion of a waterbody exceeds the biologically-based numeric temperature criteria in OAR 340-041-0028(4), the natural thermal potential temperatures supersede the biologically-based criteria, and are deemed to be the applicable temperature criteria for that waterbody. This portion of the temperature water quality standard was effective from 2003 until EPA disapproved it in response to the court decision in 2013. Many temperature TMDLs were based on this criteria, and this became the subject of a second lawsuit brought by the Northwest Environmental Advocates against EPA asserting the EPA unlawfully approved TMDLs that were based on the now disapproved Natural Conditions Criterion. The court issued a judgment on October 4, 2019, requiring DEQ and EPA to replace 15 Oregon temperature TMDLs that were based on the Natural Conditions Criterion and to reissue the temperature TMDLs based on the remaining elements of the temperature water quality standard.

This QAPP has been developed to document the analysis and numerical modeling approach that will support the `r qapp_project_area` TMDL as well as other project details. To that end, the modeling and analysis used in the previous TMDL will form the basis of the modeling approach for the TMDL replacement. In particular, this QAPP details the following:

*	Definition of the issue and objectives, including the spatial and temporal extents of the water quality impairments (Section 2);    

*	A high-level assessment of sources of pollution (Section 3);    

*	The overarching technical approach, including the appropriate modeling and analytical tools to be used (Section 4);    

*	The data sources for defining and creating inputs to the model, including data that were used in the modeling for the original TMDL. Examples of these inputs include weather, tributary stream flow and temperature, point sources and vegetation characteristics (Sections 5 and 6);    

*	How the analysis and modeling will be evaluated for acceptability (Sections 7 and 9);    

*	Scenarios for evaluating management strategies for reducing anthropogenic heat loads (Section 10);     

*	Various aspects for managing the TMDL development project, including documentation (Section 8), the project team (Section 11), data and records management (Sections 12  and 13); and    

*	Aspects relating to this QAPP and its role in the project (Sections 14  and 15).    

#	Problem Definition and Management Objectives

```{r, include=FALSE}

lookup.huc <- readxl::read_xlsx("C:/Users/ygrund/ygrund_C_Users/PROJECTS/20210504_NWMOD/Demo/data/Lookup_QAPPProjectArea.xlsx", sheet = "Lookup_QAPPProjectArea")

cat.45.rivers <- sf::st_read(dsn = "C:/Users/ygrund/ygrund_C_Users/PROJECTS/20210504_NWMOD/Demo/data/2018_2020_IR_Cat4_5_Temp_Rivers_FINAL.shp",
                             layer = "2018_2020_IR_Cat4_5_Temp_Rivers_FINAL") %>% 
  sf::st_zm() %>% 
  dplyr::left_join(lookup.huc, by = "HUC12")

cat.45.tbl <- sf::st_drop_geometry(cat.45.rivers)

pro.cat.45.tbl <- cat.45.tbl %>% 
  dplyr::filter(QAPP_Project_Area %in% qapp_project_area)

tcat5 <- pro.cat.45.tbl %>% 
  dplyr::filter(IR_categor == "Category 5") %>% 
  dplyr::group_by(AU_Name,AU_ID,Year_liste) %>% 
  dplyr::summarize(Period = toString(unique(sort(Period)))) %>% 
  dplyr::ungroup() %>% 
  dplyr::rename(`Assessment Unit Name` = AU_Name,
                `Assessment Unit ID` = AU_ID,
                `Year Listed` = Year_liste,
                `Use Period` = Period) %>% 
  dplyr::select(`Assessment Unit Name`,`Assessment Unit ID`,`Year Listed`,`Use Period`) %>% 
  dplyr::arrange(`Assessment Unit Name`,`Year Listed`)

if(NROW(tcat5)>0){
  
  tcat5 <- knitr::kable(tcat5, format = "pandoc", padding = 2,
               caption = tbls(name = "tcat5",
                              caption = paste0("Assessment units listed for temperature impairment based on Section 303(d) Category 5 in the 2018/20 Integrated Report.")))
  
}

```
`r if(NROW(tcat5)>0){tcat5}`

# Conceptual Model: Key Processes and Variables
# Technical Approach
## Overview
## Model Selection
## Software Development Quality Assessment
# Model Development
## Model Boundaries
## Spatial and Temporal Resolution
## Source Characteristics
## Data Availability and Quality
## Time Frame of Simulation
## Data Gaps
## Important Assumptions
## Model Calibration
## Model Parameters
# Model Evaluation and Acceptance
## Model Uncertainty and Sensitivity
## Model Acceptance
# Documentation in Model Reports
# Peer Review
# Management Scenarios
# Project Organization
## Project Team/Roles
## Expertise and Special Training Requirements
## Reports to Management
## Project Schedule
# Data Management
# Recordkeeping and Archiving
# QAPP Review and Approval
# Implementation and Adaptive Management
# References
